---
title: "TCGA BRCA SV Analysis"
author: "Asad"
date: "5/7/2023"
output: pdf_document
---

```{r}
library(TCGAbiolinks)
library(TCGAmutations)
library(maftools)
```

```{r}
setwd('E:/TCGA Data Analysis/CNV and SNV Analysis')
```

#Create TCGA object and read maf data
```{r}
tcga_brca=tcga_load(study = "BRCA") 
BRCA = read.maf(maf = tcga_brca@data, clinicalData = tcga_brca@clinical.data)
```


#Take a overview of the data
```{r}
plotmafSummary(maf = BRCA, rmOutlier = TRUE, addStat = 'median', dashboard = TRUE, titvRaw = T)
```

#Make oncoplot of top 10 mutated genes in BRCA
```{r}
oncoplot(maf = BRCA, top = 10)
```

#Let's make an oncoprint of BRCA1 and BRCA2 genes
```{r}
oncostrip(maf = BRCA, genes = c('BRCA1','BRCA2'))
dev.off()
```

#Let's add mutation type strip
```{r}
library(grid)
grid.rect(gp=gpar(fill=0),vp=viewport(layout.pos.col=500,layout.pos.row=300))
oncostrip(maf = BRCA, genes = c('BRCA1','BRCA2'),clinicalFeatures = 'stage_event_pathologic_stage',width(1000))
```

#Let's check the total transition and transersion mutation frequency
```{r}
titv = titv(maf = BRCA, plot = T)
```

#lollipop plot for BRCA1 gene in breast cancer.
```{r}
lollipopPlot(maf = BRCA, gene = 'BRCA1', AACol = 'HGVSp_Short', showMutationRate = TRUE)
```

#Compare mutation load with other TCGA cohort
```{r}
BRCA.mutload = tcgaCompare(maf = BRCA, cohortName = 'BRCA')
```

#Visualizing top co-occuring mutated genes
```{r}
somaticInteractions(maf = BRCA, top = 25, pvalue = c(0.05, 0.1))
```

#Detecting cancer driver genes that are frequently mutated
```{r}
BRCA.sig = oncodrive(maf = BRCA, AACol = 'HGVSp_Short', minMut = 5, pvalMethod = 'zscore')
head(BRCA.sig)
plotOncodrive(BRCA.sig)
```

#Visualizing multiple genes
```{r}
multi_genes = c("TP53", "MCM2", "BRCA1", "BRCA2", "DNMT3B", "PTEN", "STK11", "IDH1", "IDH2", "FLT3")
oncoplot(maf = BRCA, genes = multi_genes)
```




